\documentclass[12pt]{article}
\usepackage{amssymb,amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{epsfig,subfigure}
\usepackage{epstopdf}
\usepackage{bm,url}
\DeclareGraphicsExtensions{.jpg,.pdf,.png,.eps,.ps}

\textheight = 522pt
\textwidth = 450pt
\oddsidemargin 0.0in


%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}

\begin{document}

\title{CMB-S4 Collaboration Bylaws}
\maketitle

\tableofcontents

\section{Collaboration Governance Objectives/Preamble}
The CMB-S4 collaboration will carry out a CMB science program including the design and construction of the future experiment that is intended to be the definitive ground-based CMB program. CMB-S4 will deliver a highly constraining data set with which any model for the origin of the primordial fluctuations---be it inflation or an alternative theory---and their evolution to the structure seen in the Universe today must be consistent. This document outlines the CMB-S4 collaboration governance and organization of scientific activities.

\subsection{Voting Rules and Definitions}
Throughout this document, unless otherwise stated, a majority corresponds to more than one-half of the votes received, and a super-majority corresponds to more than two-thirds of the votes received. A vote of ``absent'' or an ``abstention'' does not count as a vote.

\section{Institutional Board (or Institutional Council)}

\subsection{Scope}

The Institutional Board (IB) controls the institutional aspects and the overall framework of the CMB-S4 collaboration. It is the ultimate policy forming body of the collaboration. It approves all membership issues, including the admission of new institutions into the collaboration, decides on the collaboration name and logo, sets the number of yearly collaboration meetings, organizes elections of the spokesperson and the Executive Board, develops a publications policy, appoints a publications board to approve physics results for publication, appoints a speakers board to select speakers for conferences and workshops, appoints an education and outreach board and has oversight and authority over the science policy and goals of the collaboration. The IB does not make technical decisions. The IB may change the bylaws at any time it feels it is necessary for the proper and efficient functioning of the collaboration (Section \ref{sec:amend}). The IB ratifies the Cooperative Agreements between the funding agencies and host laboratories/institutions. The IB may also establish standing and ad-hoc committees as necessary to perform its functions. Concerns of the Collaboration members are addressed to IB members who, when appropriate, bring those before the IB for its consideration. At the request of an IB member, the IB may require a detailed verbal, or written report from the Spokesperson on any action.

\subsection{Institutional Representation}

IB members will act as contacts for their institutions and inform the collaboration of any changes in personnel at their institutions. An IB member may designate another collaborator from the same institution to act as that institutions representative at any IB meeting. The CMB-S4 Spokesperson and Deputy, if they are not an IB representative, may attend all IB meetings as non-voting members except a special meeting convened to remove a Spokesperson (see Section \ref{sec:spokes}).

Each institution participating in CMB-S4 shall be represented by at most two IB members of whom one is voting whereas the other is a non-voting senior member. Each institution is responsible for choosing their own IB representative.

\subsection{IB Chair}

The IB chair is responsible for scheduling IB meetings, distributing the agendas, chairing the meetings, and distributing the minutes. The IB secretary can be delegated to take and distribute the minutes.

\subsection{Election of the IB Chair}

At the beginning of even numbered years the chair of the IB is elected from the IB membership to serve a two-year term. IB members nominate candidates by email and then vote by email, with the votes in both cases tabulated in secret by a third party. The candidate with the most votes becomes the IB chair. In case of a tie, a runoff election is held. In case of a tie in the final runoff, the chair will recuse him/herself from the vote to resolve the tie, but otherwise he/she is eligible to vote in the election. The secretary of the IB, should one be used, is chosen informally by the chairman of the IB to serve during his or her term.

\subsection{IB Meetings}

The IB meets in closed session at every CMB-S4 collaboration meeting and in extraordinary meetings held by telephone or video conference on the initiative of the IB chair or at the request of three IB representatives. IB votes require a majority of those present, unless otherwise specified in the bylaws. IB votes can be held by email, unless otherwise specified in the bylaws. Minutes of the IB meetings are distributed to IB members by the IB chair or IB secretary.

\section{Spokesperson/Deputy or Co-Spokespersons}
\label{sec:spokes}

\subsection{Scope}

The	scientific	leadership	of	the	CMB-S4	collaboration	resides	with the	spokesperson	(or	consists	of	two	
equal	co-spokespersons).			The	spokesperson	participates	actively	in	the	management	of	all	aspects	of	
the	collaboration.	They	are	expected	to	solicit	advice	from	the	collaboration	at	large	and	from	the	
executive	board	on	physics,	technical,	management,	and	leadership	issues.	The	spokesperson	is
responsible	for	the	creation	and	modification	of	management	structures	and	for	appointments	to	
leadership	positions	in	physics,	technical,	and	management	areas.	They	serve	as	the	primary	contacts	
with	a	future	host	laboratory/institution,	the	funding	agencies,	scientific	organizations,	and	the	press.
They	also	organize	and	run	the	collaboration	meetings.	The	spokesperson	may	establish	standing	and	
ad-hoc	committees	as	necessary.

\subsection{Election of a Spokesperson}

Spokespersons are elected to two-year terms. Normal spokesperson elections will be timed such that a slate of nominees can be presented at the IB meeting closest to January 1 each year. Prior to the election, qualified electors (see Article 9) are asked to nominate individuals by the IB chair. Each elector may nominate one candidate. A minimum of two nominations are required for a nominee to be eligible to appear on the slate of election candidates. After a nomination period, the IB chair will consult with the nominees to ascertain their willingness to stand for the election.

If no candidate agrees to stand for election, the terminating spokesperson will continue to serve for six months, after which a special election will be held. The term of the individual elected in a special election will be reduced by the amount needed to cause the sum of his/her term and the additional months served by the terminating spokesperson to equal two years.

The election is held by email, with votes submitted to the IB chair by qualified electors. Each candidate will provide a Candidate Statement and a short CV to the IB chair, who will collect these documents and make them available to the collaboration via the CMB-S4 internal web page prior to the balloting. The IB chair determines the detailed timing of the balloting and determines procedures for dealing with any election situations not anticipated in the bylaws. Each qualified elector votes for a single candidate for each vacant position.

The IB chair checks the ballots against the list of qualified voters and tallies the votes. If no candidate receives a majority of the votes cast, a runoff election will be held between the two candidates with the most votes. The elected candidate will take office when the IB chair announces the results of the election to the collaboration by email. In the event that the IB chair is one of the candidates, then the election will be run as detailed in this section by the IB secretary, or, if they are also a candidate, by the last elected spokesperson.

\subsection{Selection of a Deputy Spokesperson}

The Spokesperson is responsible for selecting a Deputy, with the IB concurrence, who will oversee many of the ongoing operations of the Collaboration under the direction of the Spokesperson. The Deputy will work close with and act as assistant to the Spokesperson. The Deputy must be a regular member.

\subsection{Removal of a Spokesperson}

The IB can remove a spokesperson by a secret ballot, requiring approval by at least supermajority of those present and voting at a regularly scheduled IB meeting. A two-week notice is required for a vote for removal and such a vote will be taken if at least half the IB members support such a proposal to the chair. In the event of a removal, the open position(s) will be filled following the procedures in these bylaws.

\section{Executive Board}

\subsection{Scope}

The Executive Board (EB) advises the spokesperson on scientific, financial, and organizational choices and policies. The EB also establishes procedures for making technical choices (e.g., creating technical panels) and for operating the future experiment. The EB may establish standing and ad-hoc committees as necessary to perform its functions. The EB will meet at each collaboration meeting and when requested by the spokesperson or at least two members of the EB. The deputy spokesperson is responsible for producing minutes or summaries of EB meetings, which will be made available to the CMB-S4 membership.

\subsection{EB Membership}

The EB consists of six elected members and three ex-officio members: the spokesperson and deputy spokesperson and the IB chair. The spokesperson serves as the EB chair.

\subsection{Election of EB Members}

Three members of the EB are chosen each year for a two-year term, at the IB meeting closest to January 1. Qualified electors (see Section 2) submit nominations to the IB chair prior to the election. Each collaborator may nominate one candidate per vacant position. After a nomination period, the IB chair will consult with the nominees to ascertain their willingness to stand for election. Candidates with the most nominations are listed on the ballot, until the number of candidates equals twice the number of EB vacancies. The number of candidates on the ballot may exceed twice the number of vacancies in the event that several candidates are tied with the minimum number of nominations.

The election is held by email, submitted to the IB chair by qualified electors. The IB chair determines the detailed timing of the balloting. Each qualified elector votes for as many candidates as there are vacant positions. The IB chair checks the ballots against the list of qualified electors and tallies the votes. The candidates with the highest number of votes are elected to fill all vacant positions. A runoff election is held in the event of a tie. The elected candidates will take office when the IB chair announces the results of the election to the collaboration by email.

In the first election six EB members will be elected; the three receiving the largest number of votes will serve terms of no less than three years, the others will serve terms of no less than two years. Thereafter each EB member will serve two-year terms, with three being up for election every year.

If a member of the EB resigns or becomes unable to fulfill his duties, there will be a special election to fill the vacancy. If a newly elected spokesperson is a current Executive Board member, an election for a new EB member will be held immediately following the election of the spokesperson for the remaining EB term of the new spokesperson.

The IB chair will determine procedures for dealing with any election situations not anticipated in these bylaws.

The IB may remove any EB member by the same procedures described in Article 6 for removal of a spokesperson.

\input{membership}

\section{Education and Outreach}

The CMB-S4 collaboration collectively and individually participates in and provides support for efforts in public outreach and education on subjects related to its science. The Spokesperson, with the IB concurrence, responds to requests for information from the media or may take the initiative providing material. The Spokesperson, with the IB concurrence and utilizing the advice from the Education and Outreach committee, appoints a Collaboration member to lead an education program for students and teachers at all levels. The Collaboration maintains coordination and cooperation with other ongoing education initiatives. All new scientific material to be released for purposes of public outreach or education containing other than previously published data or results must have been agreed upon by the IB and approved through the Education and Outreach Committee (Section \ref{sec:eando}).

\input{publications}

\section{Amendments to Bylaws}
\label{sec:amend}
These bylaws may be amended by the IB. A new bylaw or an amendment may be presented to the IB at one of its regularly scheduled meetings for consideration. Amendments may be introduced by any IB member or by a spokesperson. Proposed amendments will be distributed by email to the entire collaboration for their comments following this meeting. The IB will then consider the amendment for adoption at the next scheduled IB meeting. Approval of an amendment requires a super-majority vote of the IB members present.


\end{document}
