\section{CMB-S4 Authorship Policy}
\label{sec:pub}
\subsection{Scope}The authorship policy spells out the criteria and procedures for determining which members of the collaboration will be listed as authors on publications. The author list will be comprised primarily of currently active members of the collaboration that satisfy the effort and shift criteria discussed below. Former members of the collaboration that have recently left can also opt to be included as legacy authors. Procedures for adding special cases and for addressing appeals are also specified. The formulation of the author list is treated separately for physics papers and technical papers. In general, the author list for a given paper is considered frozen once the paper has been submitted. Exceptions to this are discussed in Section~\ref{sec:except}.


\subsection{Current Authors}Current authors are scientists at the level of graduate student or above who are members of the CMB- S4 collaboration and are actively engaged in the collaboration. This includes visitors. They will have contributed a significant fraction of their research time to the collaboration in the twelve months prior to preparation of the author list.

The initial set of proposed authors will be submitted to the IB by each of the IB representatives, who will prepare a list of proposed names at their institution, along with a brief description of their contributions and level-of-effort. The IB chair will circulate this initial list to the IB one month in advance of the vote. IB members who want a specific candidate discussed will submit the name of the candidate to the IB chair no less than two weeks before the vote, with any questions or issues, and that name will be flagged for discussion.

The IB chair will send the names, questions and issues regarding these candidates to all IB representatives promptly. At the initial vote, candidates who have not been flagged can be accepted by acclamation; flagged names will be discussed individually with the IB representative making the case for the candidate. A majority vote of voting members will suffice to include the candidate. This group will form the default author list for all qualifying CMB-S4 publications as defined in Section~\ref{sec:pubdef}. Individual authors can opt out of being included as an author for a given publication by notifying the spokesperson.

The current author list will be updated through this mechanism as appropriate but at least once per year, with the IB chair supervising the update. For the updates, the IB representatives will flag any new additions to the author list. Once formed, the current author list will be made available to the collaboration. Any individual member of the collaboration can petition the chair of the IB for inclusion if they believe to have been improperly excluded.

\subsection{Voting Rules}
A majority vote of those voting is required, and all authorship votes follow this rule unless otherwise noted.

\subsection{Definition of Qualifying Publications}

The current author list shall be attached to any publication, as defined in Section~\ref{sec:pubdef}, discussing a physics result, as defined in Section~\ref{sec:pubdef}. In addition, when allowed, it shall also be attached to conference proceedings.

\subsection{Legacy Authors}Legacy authors are individuals who have ceased active participation in the collaboration preceding submission of a publication but choose to opt-in to the author list via email to the spokesperson. The opt-in can either be a blanket opt-in, whereby the individual?s name is automatically included in the author list for all papers, or a case-by-case opt-in, whereby the individual must contact the spokesperson for each submitted paper. An individual can exercise his or her opt-in option until their legacy period has expired. For deceased members, the blanket opt-in option will be assumed. The legacy period, which applies to visitors as well, will be set to either one year or one-quarter of the time since the person has joined the collaboration, whichever is longer. The time a person joined shall be taken from the collaboration list as maintained by the IB chair. Once the legacy period has expired the Special Author rules apply.

\subsection{Special Authors}Special authors are defined as authors who do not qualify as current or legacy authors but are listed on an individual paper based on specific contributions to that paper. Engineering staff, technicians, undergraduates, and other non-physicists who have made exceptional contributions are examples of special authors, as well as scientists who have made significant contributions to the specific paper. They must be nominated for inclusion on the author list by a member of the IB.

Visitors, whose contact with the collaboration may encompass a period of less than one year, may be accepted as authors on papers concerning topics to which they have made significant contributions, subject to the legacy period and the approval of the IB.

For the first paper reporting, CMB-S4 individuals can either be nominated by a member of the IB, or can petition the IB chair for inclusion on the author list. In either case, both of the following conditions must be met: (1) the individual must have worked on the collaboration for at least one FTE year, and (2) the individual must have made an intellectual contribution to the collaboration. The IB must approve special author nominations and petitions by a majority vote.

\subsection{Technical Publication Authors}

Publications that discuss technical results, as defined in Section~\ref{sec:pubdef}, will not be required to carry the current author list. Publications in NIM, IEEE, SPIE on hardware, or specialized simulations are typical examples. The primary proponents of technical papers will create a custom author list that does not require approval of the collaboration. However, the draft manuscript must be submitted to the Publications Board (cf. Section~\ref{sec:pubdef}) and the author list to the IB. IB representatives can ask the proponents to add individuals they think ought be included on the author list.

\subsection{Examples of Contributions Qualifying for Authorship}

The following list gives examples of contributions; it is meant to be indicative, not exclusive, and to serve as a guideline:
\begin{itemize}\item governance of the collaboration\item construction of the experiment\item maintenance or operation of the experiment ? scientific effort during the project phase\item simulation or data reconstruction work
\end{itemize}